---
title: "Submission checks"
output: html_notebook
---

# See if there are any new requirements, policies or recommendations

* Check latest CRAN policies on http://cran.r-project.org/web/packages/policies.html
* See the CRAN checklist for package submission: https://cran.r-project.org/web/packages/submission_checklist.html
* Check for new edits in the R packages online book.

Update R, Rstudio and all dependent R packages.

* For the latter you can also use devtools::install_deps() which updates outdated dependencies.
```{r}
devtools::install_deps()
```

# Test your package again after all the updates and package modifications

* Check unit tests with devtools::test()
```{r}
devtools::test()
```

* Check coverage of all your tests with devtools::test_coverage()
```{r}
devtools::test_coverage()
```

* Check examples with devtools::run_examples()
```{r}
devtools::run_examples()
```

* Update the documentation with devtools::document() and update potential vignettes
```{r}
devtools::document()
```

* Run styler
```{r}
styler::style_pkg()
```

* Check all in local environment: devtools::check()
```{r}
devtools::check()
```

# Check reverse dependencies

* Check reverse dependencies with revdepcheck::revdep_check()
```{r}
# devtools::install_github("r-lib/revdepcheck")
revdepcheck::revdep_check(pkg = "..")
```

# Test your package on different platforms/versions on ruub

* devtools::check_rhub()
```{r}
devtools::check_rhub(pkg = "..", platforms = "fedora-clang-devel", email = "harald.puhr@gmail.com")
```

```{r}
devtools::check_rhub(pkg = "..", platforms = "ubuntu-gcc-release", email = "harald.puhr@gmail.com")
```

```{r}
devtools::check_rhub(pkg = "..", platforms = "windows-x86_64-devel", email = "harald.puhr@gmail.com")
```

* devtools::check_win_release()
```{r}
devtools::check_win_release()
```

# Check spelling errors after finalising all files

* Use spellcheck with devtools::spell_check()
```{r}
devtools::spell_check()
```

# Update cran-comments.md

* Add a summary of the new changes (from the NEWS.md file)
* Add a summary of the test environments
* Add a summary of the R CMD check results (explain ERRORs, WARNINGs, NOTEs)
* Add a summary of issues with reverse dependencies

# Run again a final local R CMD check

* devtools::check()
```{r}
devtools::check()
```


# Re-submission

* Update now the ‘Version’ field in the DESCRIPTION file
  * After the final push to Github
  * On the Github website you have still the development version (until CRAN acceptance)
  * The new version for the submission
* Replace in the NEWS.md file the development version with the new submitted version number

# Submit the package to CRAN.

* Use devtools::release() which performs more checks prior to submission

```{r}
devtools::release()
```

* Confirm submission via link in the email

# After successful submission

* Create a new release with tag version on your GitHub repo
* Copy and paste the contents of the relevant NEWS.md section into the release notes
* Increment the version of the package in the DESCRIPTION file (to X.X.X.9000)
