---
title: "doiGT"
subtitle: "Analyze distributions, internationalization, and time series of Google Trends"
author: "Harald Puhr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{doiGT}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(doiGT)
```

# Google Trends

## Brief introduction
* Short introduction to Google Trends

## Overcoming trend normalization
* Explain issue of trend normalization in Google Trends
* Explain how we circumvent this issue

# Analyze internationalization of firms

## Setup the database
* Explain how the package uses a database to store data
* Run "initialize_db()"
* Run "start_db()"
* Run "disconnect_db()"

## Download data
* Explain batch structure of downloads and computations
* Explain control and object batches

### Control data
* Use "add_control_keyword()" to create control batch
* Run "download_control()"

### Object data
* Use "add_object_keyword()" to create object batch -> list of keywords
* Run "download_object()"

### Mapping data
* Explain formula for data mapping -> references
* Run "download_mapping()"

## Compute search scores
* Run "compute_score()"

## Compute degree of internationalization
* Explain inverted gini coefficient -> references
* Run "compute_doi()"

## Additonal options
* Explain time series adjustments in "compute_score()"
* Explain HHI and entropy measures in "compute_doi()"
* Explain locations settings for all functions

# Further applications
* Explain difference between DOI and DOI-penetration -> run "download_global()"
* DOI of persons, organizations, and trends
* DOI on within-country level
